Untitled

### 2021-04-26 analysis/chapters/paper_ana_20181122.Rmd
Agrego figuras de resultados

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "../figures/",
  fig.retina = TRUE,
  # fig.height = 3,
  dev = "png",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dpi = 300
)
library(mesoda)
library(metR)
library(tidyverse)
library(lubridate)
library(data.table)
library(here)
library(patchwork)
library(unglue)
library(knitr)
library(kableExtra)

@@

```{r rcrv-sfc, fig.cap="Standar deviation of rcrv calculate for surface observations included in boxes of 2.5 degree", fig.scap=c("Wind", "Temperature")}

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_box.csv")),
      fread(here("analysis", "data", "derived_data", "rcrv_t_box.csv"))) %>%   
  # .[var %in% c("u", "v") & type %in% c(281, 287)] %>% 
  .[, type.obs := type] %>% 
  .[, type.obs := fcase(type.obs == 181, 281,
                        type.obs == 187, 287,
                        type.obs == 281, 281,
                        type.obs == 287, 287)] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 5, 0.5),
                       limits = c(0, 5),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, 
             labeller = labeller(type.obs = c("281" = "ADPSFC",
                                              "287" = "ADPSFC\n no pressure",
                                              "181" = "ADPSFC",
                                              "187" = "ADPSFC\n no pressure"),
                                 var = c("v" = "Wind",
                                         "t" = "Temperature"))) +
  labs(fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r rcrv-profile, fig.cap="Profiles of mean and standar deviation of rcrv for sounding and aircraft observations."}

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_perfil.csv")), 
      fread(here("analysis", "data", "derived_data", "rcrv_t_perfil.csv"))) %>% 
  obs.type[., on = "type"] %>%   
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(error.level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = factor(code), linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "u" = "U wind",
                                                "v" = "Wind"))) +
  labs(y = NULL,
       linetype = "",
       color = NULL) +
  theme_minimal() 
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "../figures/",
  fig.retina = TRUE,
  # fig.height = 3,
  dev = "png",
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dpi = 300
)
library(mesoda)
library(metR)
library(tidyverse)
library(lubridate)
library(data.table)
library(here)
library(patchwork)
library(unglue)
library(knitr)
library(kableExtra)
library(tagger)

@@

```{r rcrv-sfc, fig.cap="Standar deviation of rcrv calculate for surface observations included in boxes of 2.5 degree"}

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_box.csv")),
      fread(here("analysis", "data", "derived_data", "rcrv_t_box.csv"))) %>%   
  # .[var %in% c("u", "v") & type %in% c(281, 287)] %>% 
  .[, type.obs := type] %>% 
  .[, type.obs := fcase(type.obs == 181, 281,
                        type.obs == 187, 287,
                        type.obs == 281, 281,
                        type.obs == 287, 287)] %>% 
  .[, var := factor(var, levels = c("v", "t"))] %>% 
  ggplot(aes(ConvertLongitude(lon.box), lat.box)) +
  geom_raster(aes(fill = sd.y)) +
  geom_mapa() +
  scale_fill_viridis_c(breaks = seq(0, 5, 0.5),
                       limits = c(0, 5),
                       direction = -1,
                       guide = guide_colorstrip(inside = TRUE,
                                                barwidth = 20,
                                                barheight = 0.8)) +
  facet_grid(var~type.obs, 
             labeller = labeller(type.obs = c("281" = "ADPSFC",
                                              "287" = "ADPSFC\n no pressure",
                                              "181" = "ADPSFC",
                                              "187" = "ADPSFC\n no pressure"),
                                 var = c("v" = "Wind",
                                         "t" = "Temperature"))) +
  tag_facets() +
  labs(fill = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

@@

```{r rcrv-profile, fig.cap="Profiles of the mean and standard deviation of RCRV for upper-air observations.", fig.subcap=c("Sounding and aircraft observations.", "Satellite-derived wind.", "Radiances observations.")}

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_perfil.csv")), 
      fread(here("analysis", "data", "derived_data", "rcrv_t_perfil.csv"))) %>% 
  obs.type[., on = "type"] %>%   
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(error.level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = factor(code), linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "v" = "Wind"))) +
  tag_facets() +
  labs(y = NULL,
       linetype = "",
       color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

read_csv(here::here("analysis", "data", "derived_data", "rcrv_satwind.csv")) %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>%
  ggplot(aes(nivel.error, value)) +
  geom_hline(yintercept = c(0, 1), color = "darkgrey") +
  geom_line(aes(color = factor(sat_type), linetype = variable)) +
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, scales = "free_x", labeller = labeller(var = c("u" = "U wind",
                                                                   "v" = "V wind"))) +
  labs(linetype = NULL,
       color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

files <- Sys.glob("/home/paola.corrales/mesoda/analysis/data/derived_data/rcrv_*_perfil.csv")[1:6]

RCRV <- purrr::map(files, function(f) {
  meta <- unglue::unglue(basename(f), "rcrv_{sensor}_perfil.csv")

  fread(f) %>%
    .[, sensor := meta[[1]][["sensor"]]]
}) %>%
  rbindlist()

RCRV %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  setDT() %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  .[, .(value = mean(value, na.rm = TRUE)), by = .(sensor, level, variable)] %>% 
  ggplot(aes(level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sensor, linetype = variable)) +
  scale_color_discrete(labels = toupper) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  coord_flip() +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  labs(x = NULL, y = NULL,
       color = NULL, linetype = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

### Impacts of assimilated observations

```{r TQ-diff, fig.cap="Difference between experiments for the average vertical profile of variables over time.", fig.scap=c("Temperature (°C).", "Specific Humidity (g/kg)."), fig.height=3.5}
files <- list.files(derived_data, recursive = TRUE, full.names = TRUE,
                    pattern = "perfiles_ana")

perfiles <- purrr::map(files, function(f) {
  exp <- unglue(basename(f), "perfiles_{run}_{exp}.csv")
  fread(f) %>% 
    .[, exp := exp[[1]][["exp"]]]

}) %>% 
  rbindlist() %>% 
  .[, date := as_datetime(date)] %>% 
  .[date %between% c(as_datetime("2018-11-20 18:00:00"),
                     as_datetime("2018-11-23 12:00:00"))]

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "T") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)),
                         breaks = c(seq(-2, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  labs(fill = "Temperature (K)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E8_E6" = "RAD - SATWND"))) +
  tag_facets(position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "QVAPOR") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value*1000, fill = stat(level)), 
                    breaks = c(seq(-1.6, 1.6, 0.2), Inf)) +
  scale_fill_divergent_discretised(limits = c(-1.6, 1.6),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +

  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  labs(fill = "Specific humidity (g/Kg)",
       y = NULL,
       x = NULL) +
 facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E8_E6" = "RAD - SATWND"))) +
  tag_facets(tag_pool = c("d", "e", "f"), position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

```{r UV-diff, fig.cap="Difference between experiments for the average vertical profile of wind over time (shaded) and U and V (only northerly wind) profiles for the experiment with more observations (contours).", fig.height=3.5}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  # geom_contour(aes(z = value)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-2, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                breaks = seq(0, 30, 3), size = 0.2, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1,
                    size = 4, stroke = 0.1) +
  labs(fill = "U (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E8_E6" = "RAD - SATWND"))) +
   tag_facets(position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

perfiles %>% 
  dcast(lev + date ~ exp, value.var = "V") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), 
                    breaks = c(-Inf, seq(-1.6, 1.6, 0.2), Inf)) +
  scale_fill_divergent_discretised(limits = c(-1.6, 1.6),
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>% 
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                breaks = seq(-9, 0, 1), size = 0.2, linetype = 2, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>% 
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value), 
                    breaks = seq(-9, 0, 1), color = "grey30", skip = 1, 
                    size = 4, stroke = 0.1) +
  labs(fill = "V (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "AUT - CONV",
                                                         "E6_E5" = "SATWND - AUT",
                                                         "E8_E6" = "RAD - SATWND"))) +
  tag_facets(tag_pool = c("d", "e", "f"), position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3))

```{r summary-fields, fig.cap="a) Precipitable water (shaded) and northerly wind (contours, m/s), b) Average potential temperature for the PBL and c) Maximum CAPE and ~0-6 km wind shear over 15 m/s and 30 m/s for each experiment. All fields correspond to 00 UTC Nov, 22.", fig.height=10, fig.width=9}

files <- Sys.glob(paste0(derived_data, "pw/*"))[c(1, 4, 5, 7)]

dates <- c("20181122000000")

pw <- purrr::map(files, function(f) {
  details <- unglue::unglue(basename(f), "pw_ana_{exp}_{date}.nc")[[1]]

  if (details$date %in% dates) {

    ReadNetCDF(f, vars = c(value = "pw", lon = "XLONG", lat = "XLAT")) %>% 
      .[, `:=`(exp = details$exp, 
               date = lubridate::ymd_hms(details$date))] %>%
      .[]
  }
}) %>% 
  rbindlist() %>% 
  .[, c("x", "y") := wrf_project(lon, lat)]

files <- Sys.glob(paste0(derived_data, "mucape/mcape_ana_E*_20181122000000.nc"))[c(1, 4, 5, 7)]

mucape <- purrr::map(files, function(f) {
  details <- unglue::unglue(basename(f), "mcape_ana_{exp}_{date}.nc")[[1]]

  if (details$date %in% dates) {

    ReadNetCDF(f, vars = c(value = "cape_2d", lon = "XLONG", lat = "XLAT")) %>% 
      .[, `:=`(exp = details$exp, 
               date = lubridate::ymd_hms(details$date))] %>%
      setnames(old = "mcape_mcin_lcl_lfc", new = "variable") %>% 
      .[]
  }
}) %>% 
  rbindlist()

fcsts <- expand_grid(fcsts = c("20181122000000"),
                     exp = c("E2", "E5", "E6", "E8"))

ana <- lapply(seq_len(nrow(fcsts)), function(f) {

  tmp <- ReadNetCDF(paste0(derived_data, "/u_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(u = "uvmet")) %>% 
    .[, v := ReadNetCDF(paste0(derived_data, "/v_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(v = "uvmet"), out = "vector")] %>% 
    .[, q := ReadNetCDF(paste0(derived_data, "/q_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(q = "QVAPOR"), out = "vector")] %>% 
    .[, theta := ReadNetCDF(paste0(derived_data, "/theta_", fcsts[f, 1], "_", fcsts[f, 2], ".nc"), vars = c(th = "theta"), out = "vector")] %>%
    .[, date :=  ymd_hms(fcsts[f, 1])] %>% 
    .[, exp := fcsts[f, 2]] %>%  
    .[]
}) %>% 
  rbindlist()

cor <- ana[bottom_top %in% c(1, 16)] %>% 
  dcast(date + exp + south_north + west_east ~ bottom_top, value.var = c("u", "v")) %>% 
  .[, cortante := Mag(u_16 - u_1, v_16 - v_1)] %>% 
  .[, ":="(u_1 = NULL, 
           u_16 = NULL,
           v_1 = NULL,
           v_16 = NULL)]

ana[bottom_top %between% c(2, 7), .(v_mean = mean(v)), 
    by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert) +
  scale_fill_continuous_divergingx(super = ScaleDiscretised,
                       palette = "PRGn", mid = 25,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, size = stat(level)),
                proj = norargentina_lambert, color = "black", 
                breaks = c(-10, -5)) +
  scale_size_continuous(breaks = c(-10, -5), range = c(0.8, 0.4),
                        labels = c("-10", "-5")) +
  # geom_text_contour(aes(z = v_mean), size = 3, stroke = 0.05,
  #                   proj = norargentina_lambert, color = "darkorange", 
  #              breaks = c(-10, -5), skip = 0,
  #              label.placement = label_placement_n(1)) +
  # scale_linetype_manual(guide = NULL, values = c(2, 1)) +
  labs(fill = "Precipitable\nwater (Kg/m²)", size = "V (m/s)") +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

  ana[bottom_top %between% c(2, 10), .(theta_mean = mean(theta)), 
      by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  # geom_point(aes(color = v_mean)) +
  geom_contour_fill(aes(z = theta_mean, fill = stat(level_d)),
                    proj = norargentina_lambert,
                    breaks = c(-Inf, seq(290, 314, 2), Inf), limits = c(-Inf, Inf)) +
  scale_fill_distiller(super = ScaleDiscretised,
                       palette = "RdYlBu", direction = -1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  labs(fill = "Potential\ntemperature (K)") +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

  mucape %>% 
  .[variable == "mcape"] %>% 
  .[, c("x", "y") := wrf_project(lon, lat)] %>% 
  .[cor, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)), 
                    proj = norargentina_lambert, limits = c(500, 6000)) +
  scale_fill_distiller(super = ScaleDiscretised,
                       palette = "YlOrRd", direction = 1,
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  # geom_contour2(aes(z = cortante),
  #               proj = norargentina_lambert, color = "black", size = 0.4,
  #               breaks = c(10, 25)) +
  geom_contour2(aes(z = cortante, size = stat(level)),
                proj = norargentina_lambert, color = "black", 
                breaks = c(15, 30)) +
  scale_size_continuous(breaks = c(15, 30), range = c(0.8, 0.4),
                        labels = c("15", "30")) +
  # geom_point(data = ~.x[cortante >= 15 & is.cross(x, y, skip = 1)], 
  #            aes(x = lon, y = lat, 
  #                alpha = factor(cut_round(cortante, breaks = c(15, 25, Inf)))),
  #            size = 0.00002, shape = 20) +
  # scale_alpha_manual(values = c(0.3, 0.7), name = NULL, #labels = c(">5 m/s", ">15 m/s"),
  #                    guide = guide_legend(override.aes = list(size = 2))) +
  labs(fill = "MCAPE (J/Kg)", size = "Wind\nshear (m/s)") +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(1, 1, 1, 1),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3),
        strip.text = element_blank(), 
        strip.background = element_blank()) +

  plot_layout(ncol = 1, heights = c(1, 1, 1)) +
  plot_annotation(tag_levels = "a", tag_suffix = ")")
```

```{r q_vert, fig.cap="Specific humidity (g/kg, shaded) and meridional wind (m/s, contours) average over the inner domain for each latitude for 00 UTC Nov, 22."}

coord <- mucape[variable == "mcape", c("south_north", "lat")] %>% 
  .[, .(lat = mean(lat)), by = south_north]

ana[west_east %between% c(70, 180) & bottom_top %between% c(1, 25)] %>% 
  .[, .(q_mean = mean(q),
        v_mean = mean(v)), by = .(bottom_top, south_north, date, exp)] %>% 
  coord[., on = "south_north"] %>% 
  ggplot(aes(lat, bottom_top)) +
  geom_contour_fill(aes(z = q_mean*1000, fill = stat(level_d))) +
  scale_fill_distiller(super = ScaleDiscretised,
                       palette = "BrBG", direction = 1,
                       # limits = c(1, 19),
                       guide = guide_colorsteps(barwidth = 25,
                                                barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, linetype = factor(-sign(..level..))), 
                color = "grey30", size = 0.3, binwidth = 2) +
  geom_text_contour(aes(z = v_mean), color = "grey30", 
                    size = 3, stroke = 0.05, breaks = seq(-10, 6, 2),
                    label.placement = label_placement_n(1)) +
  scale_linetype(guide = NULL) +
  scale_x_latitude(breaks = seq(-40, -20, 5)) +
  facet_wrap( ~ exp, labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                                 E6 = "SATWND", E8 = "RAD"))) +
  labs(y =  "Sigma levels", fill = "Specific\nhumidity (g/Kg)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) 
```
